True versus apparent shapes of astrophysical bow shocks

### 2017-04-26 papers/Paper1/sec-conic.tex
Add the new quadric projection figs to paper
Minor change: update x0 to be negative for Ellipses
(and positive for hyperbolas)
Add the new figures into the quadrics section (sec 4)
Last changes:
+ Implement Parabolic fit for Projection
+ Thoughts about Wilkin solution for bowshocks (most useless)
+ Correct some equations in quadrics section

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization, using the convention
that if a dual sign appears, the upper sign correspond to the elliptical quadrics, and the lower sign to the hyperbolic quadrics
\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
  projected shape are developed in appendix \ref{app:parabola}}:
\begin{align}
x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
-\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi &< t < \pi \\
x_0 &= \pm a - R_0 \label{eq:x0}\\
\end{align}
Where $a$ and $b$ are real, positive numbers.

@@

\begin{align}
R_{90} = \tan\theta_c\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
\end{align}

@@

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.45\linewidth}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R0-vs-i} \\
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution.
    Variation with inclination of characteristic radii.}
  \label{fig:quadric-projection}
\end{figure*}
Once the parametrization is done, we can find the apparent shape of
the shell in the observer's frame, following the procedure explained
in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
\begin{align}
x &= a\Cos(t)-x_0 \\ 
y &= b\Sin(t)\cos\phi \\
z &=  b\Sin(t)\sin\phi
\end{align}
The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:
\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}

@@

\begin{align}
R'_0 &= \pm a' - x_0\cos i \\
R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (\pm a-R_0)\cos i
\end{align}

Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
\begin{align}
\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
\label{eq:qprime}
\end{align}
%Where $A\equiv \frac{R_c}{R_0}$
The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
\begin{align}
  \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
  \label{eq:Aprime}\\
  \tan\theta_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
  \tilde{R}'_{90} &= \frac{\left[2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q})\right]^{1/2}}{\cos i f(i;\theta_c)\frac{q'}{q}}
\end{align}
where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.

% \begin{figure*}
% \includegraphics[width=0.8\linewidth]{conic2}
% \label{fig:conic2}
% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
% \end{figure*}

Using a space of parameters like figure \ref{fig:Apqp} we can compare models with observations of real bowshocks.

%The space parameter $A'$ vs $q'$ can be seen in figure (\ref{fig:Apqp}).%In this figure is assumed that we know the intrinsic Radius of curvature and $R_0$, which is not the case with
%real observations.

>>>>

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization, using the convention
that if a dual sign appears, the upper sign correspond to the elliptical quadrics, and the lower sign to the hyperbolic quadrics
\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
  projected shape are developed in appendix \ref{app:parabola}}:
\begin{align}
x &= a\Cos(t)+x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
-\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi &< t < \pi \\
x_0 &=  R_0 \mp a \label{eq:x0}\\
\end{align}
Where $a$ and $b$ are real, positive numbers.

@@

\begin{align}
R_{90} = \left|\tan\theta_c\right|\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
\end{align}

@@

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.45\linewidth}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R0-vs-i} \\
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution.
    Variation with inclination of characteristic radii.}
  \label{fig:quadric-projection}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-vs-Rc}
  \caption{Diagnostic diagram for projected quadric parameters}
  \label{fig:projected-R90-vs-Rc}
\end{figure}
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
  \caption{Variation with inclination angle of projected quadric parameters}
  \label{fig:projected-R90-Rc-snapshots}
\end{figure*}
Once the parametrization is done, we can find the apparent shape of
the shell in the observer's frame, following the procedure explained
in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
\begin{align}
x &= a\Cos(t)+x_0 \\ 
y &= b\Sin(t)\cos\phi \\
z &=  b\Sin(t)\sin\phi
\end{align}
The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:
\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}

@@

\begin{align}
R'_0 &= \pm a' + x_0\cos i \\
R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} +  (R_0 \mp a)\cos i
\end{align}

Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
\begin{align}
\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
\label{eq:qprime}
\end{align}
%Where $A\equiv \frac{R_c}{R_0}$
The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
\begin{align}
  \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
  \label{eq:Aprime}\\
  \tan\theta'_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
  \tilde{R}'_{90} &= \left(\frac{2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q}}{\frac{q'}{q}}\right)^{1/2}\frac{\sec i}{f(i;\theta_c)}
\end{align}
where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.

When $R'_{90}$ is measurable, diagnostic diagrams like figure (\ref{fig:projected-R90-vs-Rc}) can be used to compare with observations.
